Child survival for mothers: mortality change and related measures

### 2020-05-01 ALAP2020/ALAP.Rmd

@@

Following @Coresh1988 we can express the fertility component in a multiplicative way with variability in the level but not in the shape, as ${m(k)}_x = F_\beta\,k\,r_x$, where $F_\beta$ is the baseline accumulated fertility, $K$ is a random variable with mean 1 that allows variability between groups and $r_x$ is the fertility structure by age ($\int_{0}^{\beta}{r_x}=1$). Frailty part can be thought in a cohort effect way, also in the multiplicative assumption as @Vaupel2014, with $l(z)_x=e^{-H_{x}Z}=l_x^Z$, with baseline hazard $\mu$. Replacing conveniently the last two expressions and considering the joint distribution $f_{kz}=f_{z/k} \,f_k$, the mean $\overline{CS}_a$ would be:

@@

>>>>

The second Taylor´s term is null because $\int_{\alpha}^a{x \, m_{x}dx} = \kappa \, F_a$. The formula tells us that the survival experience for a woman aged *a* depends mainly of cumulated fertility (possible cases, different from the ancestor count case where this doesn´t affect) and child survival probability (success cases), but also negative proportional affected by how disperse is the fertility by age (variance \sigma^2) and the suvival curvature around (negative sign), in a $l_x$ range where is tipycally very flat (range 20-40 years old) in transitioned populations. Guatemala improved the approximation with years due to rectangularization process in $l_x$ (figure \@ref(fig:plot_CS_aprox)). And change in $\kappa$, taking logs and deriving: $\frac{dCS_a}{d\kappa}\frac{1}{CS_a} \approx \mu_{a-\kappa}F_a \Delta\kappa$

@@

Following @Coresh1988 we can express the fertility part in a multiplicative way with variability in the level but not in the shape, as ${m(k)}_x = F_\beta\,k\,r_x$, where $F_\beta$ is the baseline cumulated fertility, $K$ is a random variable with mean 1 that allows variability between groups and $r_x$ is the fertility structure by age ($\int_{0}^{\beta}{r_x}=1$). Frailty part can be thought in a cohort effect way, also in the multiplicative assumption as @Vaupel2014, with $l(z)_x=e^{-H_{x}Z}=l_x^Z$, with baseline hazard $\mu$. Replacing conveniently the last two expressions and considering the joint distribution $f_{kz}=f_{z/k} \,f_k$, the unconditional mean $\overline{CS}_a$ would be:

@@

given K and Z values are fertility and child survival are independent
K is a partity level assgined to cohorts of women.
